---
title: "Causal Effect"
author: "Roshan Ranganathan"
format: html
execute: 
  echo: false
---

```{r}
#| message: FALSE
library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)
```

```{r}
ch6 <- trains |>
  select(att_end, treatment)
```

We’ve defined our research question: the effect of exposing individuals in Chicago to Spanish-speakers on their attitudes toward immigration. After creating a Preceptor Table and ensuring our data aligns with it, we focused on Justice in data science, emphasizing stability, representativeness, and unconfoundedness. Despite the political landscape shifts since 2012, making past data less reliable, we proceeded by comparing observations from Boston train commuters with our Preceptor Table. Courage in data analysis involved refining models to create a reliable Data Generating Mechanism. We estimated an average treatment effect of exposure on immigration attitudes, finding an average shift of 1.5 units with a 95% Confidence Interval from 0.5 to 2.5 units, nearly as significant as the difference between Democrats and Republicans in the control group.

```{r}
#| cache: TRUE
fit_gauss <- brm(formula 
= att_end ~ treatment, data = ch6, family = gaussian(), refresh = 0, silent = 2, seed = 9)
```


```{r}
tbl_regression(fit_gauss)
```

```{r}
ndata <- tibble(treatment = c("Treated", "Control"))
```

```{r}
fit_gauss |> 
  add_epred_draws(
    newdata = ndata) |>
    select(treatment, .draw, .epred) |>
    pivot_wider(id_cols = .draw, names_from = treatment, values_from = .epred) |>
    mutate(causal_effect = Treated - Control) |>
    select(- .draw) |>
    ggplot(aes(x = causal_effect)) +
    geom_histogram(aes(y = after_stat(count / sum(count))), bins = 100) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_classic() +
    labs(title = "Posterior for Average Treatment Effect",
    subtitle = "Exposure to Spanish-speakers shifts immigration attitudes rightward",
    x = "Difference in Attitude",
    y = "Probability")
```


